|

### 2021-06-01 appendix/appendix.Rmd
changes to appendix, article, R script

---
title: |
       | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
author:
- "Huzeyfe Alptekin[^alptekin]"
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "Catarina Roman[^roman]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

[^alptekin]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.

[^freire]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.

[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.

[^roman]: PhD Student, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

@@

# A Brief Introduction to the Law of _1/n_ and the Reverse Law of _1/n_

In this section, we present the intuition behind the _law of 1/n_, as well as the alternative _reverse law of 1/n_ proposed by @primo2008distributive.

@@

In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$, and there are convex costs associated with the project.\footnote{Concave means that $b'>0$ and $b''<0$. Convex means that $c'>0$ and $c''>0$. We assume that the derivatives are well defined throughout the analysis. Moreover, we drop the constituency index to make the model more intuitive, so the reader should assume that we always employ a symmetric Nash equilibrium.} The first type of cost, $c_1(x)$, comprises the expenses within the constituency (e. g., hiring a local company for the project). The second type of cost, $c_2(x)$, captures the expenses outside the constituency (e. g., hiring a company from another state). Finally, the third cost, $c_3(x)$, captures the externalities generated by the project (e. g., how much prices shift because local economic factors are being used to provide the project). The total cost is equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$. The tax burden generated by the project is equal to $T(x) = c_1(x) + c_2(x)$.

Projects are economically efficient when the marginal costs are equal to the marginal benefits of the project size. This leads to the economic optimal project size, $x^E$. The optimal project size is $b'(x^E) - c_1'(x^E) - c_2'(x^E) - c_3'(x^E) = 0$. However, the projects that are actually implemented have a different structure. First, assume that the constituency in question has a tax burden $t = 1/n$, where $n$ represents the number of constituencies. Also, suppose that benefits are distorted by the fact that costs within the constituency ($c_1(x)$) become investments in local firms. Therefore, the costs and benefits of implementing a project with size $x$ have the following structure:

@@

Note that the numerator is always positive, as the marginal investment costs inside and outside the district increase according to the project size. The _law of 1/n_ holds when the denominator is negative. $b''(x) < 0$ by assumption, and $-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x) < 0$ as $c_1'', c_2'', c_3'' > 0$. Then, the _law of 1/n_ is true when $c_1''(x)$ is smaller than $n^{-1}[c_1''(x) + c_2''(x)] + c_3''(x) - b''(x)$.

As the above condition suggests, the _law of 1/n_ holds only in specific situations. @primo2008distributive advance that theory by considering other situations where the _law_ may not hold, and they also argue that there are cases in which a _reverse law of 1/n_ holds, that is, larger legislatures may lead to lower public expenditures.

Following @primo2008distributive, let $n$ be the number of districts, $m$ the number of citizens in each district, and $nm$ is the total population in the country. Consider a local public good that generates a per capita benefit of $b(x, m) = x^\alpha m^{\beta-1}$ according to size $x$, where $\beta$ is the degree of congestion of the public good, that is, how much the addition of individuals reduce the benefits for other individuals (note that the lower the $\beta$, the higher the congestion). In terms of costs, consider a linear cost function $C(x) = x$, and in terms of taxation, assume that the people in the district pay both local and federal government taxes. The degree that taxes are shared is denoted by $s$. Moreover, there is a deadweight loss of the taxes $\theta \geq 1$. The tax then becomes: $t = \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta$. Therefore, the citizens receive the following net benefit of a project with size $x$:

@@

curve(xstar(x, beta = 0.35, theta = 0.8), from = 10, to = 20,
      main = 'Increasing project size when varying legislature size \n (high deadweight losses)', xlab = 'Project Size', ylab = 'Number of Districts (legislature size)')
curve(xstar(x, beta = 0.35, theta = 0.5), from = 10, to = 20,
      main = 'Decreasing project size when varying legislature size \n (low deadweight losses)', xlab = 'Project Size', ylab = 'Number of Districts (legislature size)')
```

Thus, we see that both the _law of 1/n_ and its reverse formulation are equally plausible. Here we show how the results change just by changing the levels of deadweight losses, but authors have suggested other reasons why the _law of 1/n_ may not apply, such as bicameralism [@chen_malhotra_2007], popular initiatives [@matsusaka2005endogeneity], type of government [@coate2011government], supermajorities [@lee2015supermajority], political fragmentation [@lledo2003electoral], and ideology [@bjedov2014impact].

@@

We webscraped three large academic databases: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736). The `R` script we wrote extracted the article title, abstract, authors, year, journal of publication, and database from which the record originated. Our code is available in the `R` script available in this repository. We screened these results with an English language and article restriction, that is, we excluded all records written in other languages and all that were not academic papers, such as book chapters or doctoral theses. We set no restriction to unpublished articles.

We complemented this process by doing a term search on Google Scholar after having finished the entire eligibility procedure in the first sample. We formulated the search string based on the terms and expressions that appeared most frequently in the articles included in our meta-analysis. The choice of string translates the central point of our inquiry: the relationship between legislature size and public spending. The search string was as follows: `("upper chamber size" OR "lower chamber size" OR "council size" OR "parliament size" OR "legislature size" OR "number of legislators" OR "legislative size") AND ("spending" OR "expenditure" OR "government size")`. We scraped Google Scholar on March 5^th^, 2021. Using the titles of this new database's records, we did a fuzzy matching with the database of @weingast1981political citations mentioned previously. We then performed the exact same eligibility procedures, further explained below. This resulted in 3,041 additional records. Combining the two search strategies, we assessed a total of 5,705 records.

@@

The third phase consisted of filling out tables for each of the remaining 47
articles to systematically evaluate their eligibility. Since authors use
different measures for government spending and the number of lower/upper house
members, we extracted all coefficients that provided this information. In this
phase, we also collected information on whether the paper had been published,
and if it explicitly discussed the _law of 1/n_. Upon choosing the variables,
we excluded two studies from the first sample, as they did not have the
dependent/independent variables we collected for our meta-analysis. We then
included the 2 papers we found in the second search, as both conformed to our
criteria, and compiled our final sample of `r length(unique(dat$authoryear))`
articles.

@@

We selected the final pool of articles based on two criteria, namely the treatment and the outcome variables employed in the paper. The categories follow below:

1.  Treatment variables:

-   *N*: Number Legislators in the Lower House
-   *logN*: Log Number Legislators in the Lower House
-   *K*: Number Legislators in the Upper House

2.  Outcome variables:

-   *ExpPC*: Expenditure Per Capita
-   *logExpPC*: Log Expenditure Per Capita
-   *PCTGDP*: Percent GDP Public Expenditure

@@

```{tikz tikz-ex, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.cap = "PRISMA Flow Chart for First Search Strategy: Weingast et al. Citations"}
\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
  \footnotesize
  \linespread{1.0}

@@

\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 28)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);

 \end{tikzpicture}
```

```{tikz tikz-ex2, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.width=5, fig.height=2, fig.cap="PRISMA Flow Chart for First Search Strategy: Search String with Terms"}
\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
  \footnotesize
  \linespread{1.0}
  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Screening 1}};
  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening 2}};
  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};
  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};
  \node (id) [phase, right of = ID, xshift = 1cm] {Clean records identified through webscraping  \\ \textbf{(n = 3041)}};
  \node (1st) [exc, right of = id, xshift = 3cm] {Records excluded after reading title, or in languages other than English, book chapters, doctoral theses, and duplicates \\ \textbf{(n = 2603)}};
  \node (screen) [phase, below of = id] {Abstracts assessed for Eligibility \\ \textbf{(n = 483)}};
  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading abstract \\ \textbf{(n = 339)}};
  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 99)}};
  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 86)}};
  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 13)}};
  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 11)}};
\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 2)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);
 \end{tikzpicture}
```

@@

The average year of publication in our sample is `r round(mean(dat$year), 2)` with standard deviation of `r round(sd(dat$year), 2)`. The oldest study included in the paper is from `r min(dat$year)`, while the most recent paper was written in `r max(dat$year)`. Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the *law of 1/n*.

@@

```{r, fig.width=4, fig.height=2.5, fig.cap="Was the study published?", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) +
    geom_bar(color = "black") +
  labs(x = "Published Study?",
       y = "") +
  theme_bw()
```

@@

Our sample differs considerably in regards to research design. One remarkable difference is that several authors apply the logics of the *law of 1/n*, which was built with majoritarian systems in mind, to non-majoritarian democracies. In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that for the \textit{law of 1/n} to be valid in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, votes are geographically concentrated. The concentration facilitates politicians to use pork-barrel projects to captivate their electoral supporters.}

```{r, fig.width=6, fig.height=3, fig.cap="Electoral Systems", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, elecsys2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(elecsys2))) +
    geom_bar(color = "black") +
  labs(x = "Electoral Systems",
       y = "") +
  theme_bw()
```

@@

The outcome variables included in the paper are:

-   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[1])` Per Capita Expenditure papers
-   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[2])` Expenditure as a Percentage of the GDP papers
-   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[3])` Natural Log of Per Capita Expenditure papers

```{r, fig.width=6, fig.height=2.3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "Dependent Variables") +
  coord_flip() +
  theme_bw()
```

@@

Most papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(dat$indepvar2)[3])`). The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(dat$indepvar2)[1])`). Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(dat$indepvar2)[2])`). As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[1]`, while the number of papers is only `r length(unique(dat$id))`.

```{r, fig.width=6, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", echo = FALSE, cache=TRUE}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
                                                  "Log N",
                                                  "N (lower house legislators)"
                                                  ))) %>%
  ggplot(aes(x = indepvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "Independent Variables") +
  coord_flip() +
  theme_bw()
```

@@

One simple statistic that we can compute to assess the validity of the *law of 1/n* is the frequency of positive and negative estimates in the study sample. Below we plot the frequency for all the papers included in the meta-analytic dataset.

```{r, size="footnotesize", fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE, echo = FALSE}
dat %>%
  ggplot(aes(x=as.factor(scoef))) +
  geom_bar(color = "black") +
  labs(x = "Coefficient Sign",
       y = "") +
  theme_bw()
```

@@

We chose a set of moderators that frequently appear in the literature and may help us interpret our results. We included them in our meta-regressions alongside an indicator for the type of independent variable used in the original study ($n$, log($n$), or $k$). The additional moderators are: electoral system; estimation method; publication year; paper publication in an academic journal.

```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published) %>%
  rename(`Independent Variables` = indepvar2,
         `Electoral system`      = elecsys2,
         `Estimation method`     = method,
         `Year`                  = year,
         `Published work`        = published)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```

@@

The *law of 1/n* posits that we should expect a positive influence of legislature size on public expenditures. A general test of the theory could investigate whether the papers tend to find a higher frequency of positive coefficients in their estimations. In statistical terms, consider a random variable representing the coefficient sign for the papers. As each sign of the paper is a Bernoulli trial, the aggregate result for all papers follows a Binomial distribution with parameters $n$ equals the number of papers, and $p$ the chance of a positive sign. The *law of 1/n* can be reformulated as the chance of $p>0.5$, which facilitates the testing of the theory. The null hypothesis for such a test is that:

@@

As we are taking an agnostic approach, we acknowledge that either the *law of 1/n* ($p>0.5$), or the *reverse law of 1/n* ($p<0.5$) may be true. In this case, the alternative hypothesis is $p\neq 0.5$. To perform this test, we run binomial tests in `R`, using the function `binom.test(.)`.

>>>>

---
title: |
       | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
author:
- "Huzeyfe Alptekin[^huzeyfe]"
- "Danilo Freire[^danilo]"
- "Umberto Mignozzetti[^umberto]"
- "Catarina Roman[^catarina]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

[^huzeyfe]: Independent Researcher, <huzeyfealptekin@gmail.com>.

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.

[^catarina]: PhD Student, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

@@

# A Brief Introduction to the "Law of _1/n_" and the "Reverse Law of _1/n_"

In this section, we present the intuition behind the "law of $1/n$", as well as
the alternative "reverse law of $1/n$" proposed by @primo2008distributive.

@@

In their model, every local public goods project of size $x$ generates a
concave benefit $b(x)$, and there are convex costs associated with the
project\footnote{The concavity assumption implies that $b'>0$ and $b''<0$. A
similarly convex assumption would mean that $c'>0$ and $c''>0$. We assume that
the derivatives are well defined throughout the analysis. Moreover, we drop the
constituency index to make the model more intuitive, so the reader should
assume that we always employ a symmetric Nash equilibrium.}. The first type of
cost, $c_1(x)$, comprises the expenses within the constituency (e. g., hiring a
local company for the project). The second type of cost, $c_2(x)$, captures the
expenses outside the constituency (e. g., hiring a company from another state).
Finally, the third cost, $c_3(x)$, captures the externalities generated by the
project (e. g., how much prices shift because local economic factors are being
used to provide the project). The total cost is equal to $c(x) = c_1(x) +
c_2(x) + c_3(x)$. The tax burden generated by the project is equal to $T(x) =
c_1(x) + c_2(x)$.

Projects are economically efficient when the marginal costs are equal to the
marginal benefits of the project size. This leads to the economic optimal
project size, $x^E$, which is defined as $b'(x^E) - c_1'(x^E) - c_2'(x^E) -
c_3'(x^E) = 0$. However, the projects that are actually implemented have a
different structure. First, assume that the constituency in question has a tax
burden $t = 1/n$, where $n$ represents the number of constituencies. Also,
suppose that benefits are distorted by the fact that costs within the
constituency ($c_1(x)$) become investments in local firms. Therefore, the costs
and benefits of implementing a project with size $x$ have the following
structure:

@@

Note that the numerator is always positive, as the marginal investment costs
inside and outside the district increase according to the project size. The
"law of $1/n$" holds when the denominator is negative. $b''(x) < 0$ by
assumption, and $-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x) < 0$ as $c_1'', c_2'',
c_3'' > 0$. Then, the _law of 1/n_ is true when $c_1''(x)$ is smaller than
$n^{-1}[c_1''(x) + c_2''(x)] + c_3''(x) - b''(x)$.

As the above condition suggests, the "law of $1/n$" holds only in specific
situations. @primo2008distributive advance that theory by considering other
situations where the "law" may not hold, and they also argue that there are
cases in which a "reverse law of $1/n$" may exist, that is, where larger
legislatures may lead to lower public expenditures.

Following @primo2008distributive, let $n$ be the number of districts, $m$ the
number of citizens in each district, and $nm$ the total population in the
country. Consider a local public good that generates a per capita benefit of
$b(x, m) = x^\alpha m^{\beta-1}$ according to size $x$, where $\beta$ is the
degree of congestion of the public good, that is, how much the addition of
individuals reduce the benefits for other individuals (note that the lower the
$\beta$, the higher the congestion). In terms of costs, consider a linear cost
function $C(x) = x$, and in terms of taxation, assume that the people in the
district pay both local and federal government taxes. The degree that taxes are
shared is denoted by $s$. Moreover, there is a deadweight loss of the taxes
$\theta \geq 1$. The tax then becomes: $t = \left(\dfrac{(n – ns + s)x + (ns –
s)X}{nm}\right)^\theta$. Therefore, the citizens receive the following net
benefit of a project with size $x$:

@@

curve(xstar(x, beta = 0.35, theta = 0.8), from = 10, to = 20,
      main = 'Increasing project size when varying legislature size \n (high deadweight losses)', xlab = 'Legislature Size', ylab = 'Project Size')
curve(xstar(x, beta = 0.35, theta = 0.5), from = 10, to = 20,
      main = 'Decreasing project size when varying legislature size \n (low deadweight losses)', xlab = 'Legislature Size', ylab = 'Project Size')
```

Thus, we see that both the "law of $1/n$" and its reverse formulation are
equally plausible. Here we show how the results change just by changing the
levels of deadweight losses, but authors have suggested other reasons why the
"law of $1/n$" may not apply, such as bicameralism [@chen2007law], popular
initiatives [@matsusaka2005endogeneity], type of government
[@coate2011government], supermajorities [@lee2015supermajority], political
fragmentation [@lledo2003electoral], and ideology [@bjedov2014impact].

@@

We webscraped three large academic databases:
\href{https://scholar.google.com/}{Google Scholar} (n = 1001);
\href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and
\href{https://www.scopus.com/}{Scopus} (n = 736). The `R` script we wrote
extracted the article title, abstract, authors, year, journal of publication,
and database from which the record originated. Our code is in the `R` script
available in this repository. We then filtered these results and selected only
articles that were written in English. While we included unpublished papers in
our search, we excluded book chapters and doctoral theses from our sample.

We complemented this process by doing a term search on Google Scholar after
having finished the entire eligibility procedure in the first sample. We
formulated the search string based on the terms and expressions that appeared
most frequently in the articles included in our meta-analysis. The choice of
string translates the central point of our inquiry: the relationship between
legislature size and public spending. The search string was as follows:
`("upper chamber size" OR "lower chamber size" OR "council size" OR "parliament
size" OR "legislature size" OR "number of legislators" OR "legislative size")
AND ("spending" OR "expenditure" OR "government size")`. We scraped Google
Scholar on March 5^th^, 2021. Using the titles of this new database's records,
we fuzzy-matched those articles with the database of @weingast1981political
citations mentioned previously to check for duplicates. We then performed the
exact same eligibility procedures, further explained below. This resulted in
3,041 additional records. Combining the two search strategies, we assessed a
total of 5,705 records.

@@

The third phase consisted of filling out tables for each of the remaining 
articles to systematically evaluate their eligibility. Since authors use
different measures for government spending and the number of lower/upper house
members, we extracted all coefficients that provided this information. In this
phase, we also collected information on whether the paper had been published,
and if it explicitly discussed the "law of $1/n$". Upon choosing the variables,
we excluded two studies from the first sample, as they did not have the
dependent/independent variables we collected for our meta-analysis. We then
included the 2 papers we found in the second search, as both conformed to our
criteria, and compiled our final sample of `r length(unique(dat$authoryear))`
articles.

@@

We selected the final pool of articles based on two criteria, namely the independent and the dependent variables employed in the paper. The categories follow below:

1.  Independent variables:

-   *N*: Lower Chamber Size
-   *logN*: Log Lower Chamber Size
-   *K*: Upper Chamber Size

2.  Dependent variables:

-   *ExpPC*: Expenditure Per Capita
-   *logExpPC*: Log Expenditure Per Capita
-   *PCTGDP*: Expenditure as Percentage of GDP

@@

```{tikz tikz-ex, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.height=2, fig.cap = "PRISMA Flow Chart for First Search Strategy: Weingast et al. Citations"}
\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
\scalebox{0.9}{
  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
  \footnotesize
  \linespread{1.0}

@@

\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 28)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);
 \end{tikzpicture}
}
```

```{tikz tikz-ex2, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.cap="PRISMA Flow Chart for First Search Strategy: Search String with Terms"}
\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
\scalebox{0.9}{
  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
  \footnotesize
  \linespread{1.0}
  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Screening 1}};
  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening 2}};
  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};
  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};
  \node (id) [phase, right of = ID, xshift = 1cm] {Clean records identified through webscraping  \\ \textbf{(n = 3041)}};
  \node (1st) [exc, right of = id, xshift = 3cm] {Records excluded after reading title, or in languages other than English, book chapters, doctoral theses, and duplicates \\ \textbf{(n = 2603)}};
  \node (screen) [phase, below of = id] {Abstracts assessed for Eligibility \\ \textbf{(n = 483)}};
  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading abstract \\ \textbf{(n = 339)}};
  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 99)}};
  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 86)}};
  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 13)}};
  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 11)}};
\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 2)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);
 \end{tikzpicture}
}
```

@@

The average year of publication in our sample is `r round(mean(dat$year), 2)`
with standard deviation of `r round(sd(dat$year), 2)`. The oldest study
included in the paper is from `r min(dat$year)`, while the most recent paper
was written in `r max(dat$year)`. Therefore, we cover 
`r max(dat$year)-min(dat$year)` years of tests of the "law of $1/n$".

@@

```{r, fig.width=4, fig.height=2.5, fig.cap="Was the study published?", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  theme_bw()
```

@@

Our sample differs considerably in regards to research design. One remarkable
difference is that several authors apply the logics of the "law of $1/n$", which
was built with majoritarian systems in mind, to non-majoritarian democracies.
In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])`
of the papers study *Majoritarian* systems while 
`r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study
*Non-Majoritarian* electoral systems\footnote{Note that for the "law of
$1/n$" to be valid in a non-majoritarian system, we need to assume that despite
the fact that politicians are able to campaign in every place in the district,
votes are geographically concentrated. The concentration facilitates
politicians to use pork-barrel projects to captivate their electoral
supporters.}.

```{r, fig.width=6, fig.height=3, fig.cap="Electoral Systems", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, elecsys2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(elecsys2))) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  theme_bw()
```

@@

The dependent variables included in the paper are:

-   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[1])` Expenditure Per Capita papers
-   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[2])` Expenditure as a Percentage of the GDP papers
-   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[3])` Log of Expenditure Per Capita papers

```{r, fig.width=6, fig.height=2.3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Expenditure Per Capita",
                                     "Expenditure as Percentage GDP",
                                     "Log Expenditure Per Capita"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

Most papers in our sample analyse the number of legislators in the lower
chamber (`r as.numeric(table(dat$indepvar2)[3])`). The second most frequent
independent variable is the number of legislators in the upper chamber 
(`r as.numeric(table(dat$indepvar2)[1])`). Finally, the minority of papers use the
natural log of the number of legislators in the lower chamber as an independent
variable (`r as.numeric(table(dat$indepvar2)[2])`). As we noted above, some
papers had multiple coefficients, and thus the total number of coefficients is
`r dim(dat)[1]`, while the number of papers is only `r length(unique(dat$id))`.

```{r, fig.width=6, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", echo = FALSE, cache=TRUE}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, 
                            labels = c("Upper Chamber Size",
                                       "Log of Lower Chamber Size",
                                       "Lower Chamber Size"
                                                  ))) %>%
  ggplot(aes(x = indepvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

One simple statistic that we can compute to assess the validity of the "law of
$1/n$" is the frequency of positive and negative estimates in the study sample.
Below we plot the frequency for all papers included in the meta-analytic
dataset.

```{r, size="footnotesize", fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE, echo = FALSE}
dat %>%
  ggplot(aes(x=as.factor(scoef))) +
  geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  theme_bw()
```

@@

We chose a set of moderators that frequently appear in the literature and may
help us interpret our results. We included them in our meta-regressions
alongside an indicator for the type of independent variable used in the
original study: lower chamber size; natural logarithm of lower chamber size; or
upper chamber size. The additional moderators are: publication year; whether
the paper was published in an academic journal; the estimation method used in
the paper; the institutional design in terms of the division of legislative
power; and the electoral system.

```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, year, published, method,
              instdesign, elecsys2) %>%
  mutate(indepvar2 = recode(indepvar2,
                            `N` = "Lower Chamber Size",
                            `K` = "Upper Chamber Size",
                            `logN` = "Log of Lower Chamber Size"),
         elecsys2 = recode(elecsys2,
                           `Non-Maj` = "Non-Majoritarian",
                           `Maj` = "Majoritarian")) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)
export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```

@@

The "law of $1/n$" posits that we should expect a positive influence of
legislature size on public expenditures. A general test of the theory could
investigate whether the papers find a higher frequency of positive coefficients
in their estimations. In statistical terms, consider a random variable
representing the coefficient sign for the papers. As each sign of the paper is
a Bernoulli trial, the aggregate result for all papers follows a Binomial
distribution with parameters $n$ equals the number of papers, and $p$ the
chance of a positive sign. The "law of $1/n$" can be reformulated as the chance
of $p>0.5$, which facilitates the testing of the theory. The null statistical
hypothesis for such a test is that:

@@

We take an agnostic approach and acknowledge that either the "law of $1/n$"
($p>0.5$), or the "reverse law of $1/n$" ($p<0.5$) may be true. In this case,
the alternative hypothesis is $p \neq 0.5$. To perform this test, we run
binomial exact tests in `R`, using the function `binom.test(.)`.
